---
title: "Assignment 5: Data Transform, Tidying and Munging"
output: html_notebook
---

1. Save this Rmd file as 'assignment5_yourfirstname_yourlastname.Rmd` (e.g., assignment5_youngjin_lee.Rmd).
  - Make sure to remove all testing code chunks.
  - Make sure to test reproducibility of your Rmd file.
2. Submit your Rmd file to Canvas. 

```{r message=FALSE}
library(tidyverse)
```


### Load scorecard.csv file

- Create a tibble named `scorecard` from the `scorecard.csv` file
  - `scorecard.csv` is available in Canvas
- Review [scorecard documentation](https://rdrr.io/github/uc-cfss/rcfss/man/scorecard.html) to learn about the data set

```{r}
scorecard <- read.csv("scorecard.csv")
head(scorecard)
```

### 1. Find TX institutions that has more than 50% of first-generation students (1 point)

- Order institutions by first-generation student percentage
- Select top ten TX institutions that has more than 50% of first-generation students
  - If there is a tie, you will get more than 10 institutions. 
- Show the content of a tibble with institution name and first generation fraction columns

```{r}
scorecard %>%
  arrange(desc(firstgen))%>%
  filter(state=="TX" , firstgen > 0.5)%>%
  select(name, firstgen, num_range("firstgen", 1:10))
```

### 2. Find the number of instituions that has more than 50% of first-generation students in each state, and show state name and number of institutions institutions in the descening order of the number of such institutions (1 point)

- Show the content of tibble with two columns, state name and number of institutions satisfying the given condition (more than 50% of first-generation students)

```{r}
scorecard %>%
  arrange(desc(firstgen))%>%
  filter(firstgen > 0.5)%>%
  count(state)%>%
  arrange(desc(n))
```

### 3. Create a data frame with the 20 most expensive colleges (1 point)

- Show the content of a tibble with rows satisfying conditions
- Order the result in the decreasing order of cost

```{r}
scorecard %>%
  arrange(desc(cost))%>%
  slice(1:20)
```

### 4. Find the median value of the cost of attendance of public colleges in each state that has more than 50% of first generation student (2 points)

- Rearrange the resulting data frame in the decreasing order of median annual cost of attendance.
- Show the content of a tibble with two columns, state name, median cost of colleges meeting the condition

```{r}
scorecard %>%
  filter(firstgen > 0.5 , type == "Public")%>%
  group_by(state)%>%
  summarise(state, median_cost=median(cost))%>%
  arrange(desc(median_cost))%>%
  distinct()
```

### 5. Create a data frame showing the average admission rate, the average SAT score and the average cost of attendance of top 5 institutions of each type (2 points)

- For each institution category (Public; Private, nonprofit; Private, for-profit), you need to identify five institutions with highest average SAT scores.
- Then, compute the average admission rate, SAT score and cost of attendance of those five institutions in the institution category


```{r}
scorecard %>%
  group_by(type)%>%
  arrange(desc(satavg))%>%
  slice(1:5)%>%
  group_by(type)%>%
  summarise(type, avg_admrate=mean(admrate), avg_satavg=mean(satavg), avg_cost=mean(cost))%>%
  distinct()
```

### 6. Create a scatter plot of avg. cost of attendance vs. avg. debt of college students in each state (3 points)

- Use different colors for each state 
- Show one linear regression line for data points. 
- Use `Average Cost of Attendance` for X axis label
- Use `Average Debt When Graduating` for Y axis label

```{r}
scorecard %>%
  group_by(state)%>%
  summarise(avg_cost=mean(cost, na.rm=TRUE), avg_debt=mean(debt, na.rm=TRUE))%>%
  ggplot(aes(avg_cost,avg_debt))+
  geom_point(aes(avg_cost, avg_debt, color=state)) + 
  geom_smooth(method = "lm") +
  xlab("Average Cost of Attendance")+
  ylab("Average Debt When Graduating")
  
```

### 7. Using `race` data set, creates a line graph showing temporal changes of student scores (3 points). 

- X axis is Time
- Y axis is Score
- Use different colors and shapes for each student.

### Load the `race.csv` file to create a tibble named `race`

```{r}
race <- read.csv("race.csv")
race%>%
  pivot_longer(X50:X350,
               names_to = "Time_str",
               values_to = "Score")%>%
  mutate(Time=as.numeric(substr(Time_str, 2, nchar(Time_str))))%>%
  group_by(Time)%>%
  ggplot(aes(Time, Score, color=Name, shape=Name))+
  geom_point()+
  geom_line()+
  xlab("Time")+
  ylab(("Score"))
```

