---
title: "Assignment 4: Data transformation using dplyr"
output: html_notebook
---

1. Save this Rmd file as 'assignment4_yourfirstname_yourlastname.Rmd` (e.g., assignment4_youngjin_lee.Rmd).
2. Provide R codes that will create a data frame or generate each ggplot outcomes shown in the `assignment4_expected_results.html` file.
3. Submit your Rmd file and rendered HTML report file to Canvas. 
  - Make sure to submit a **clean** Rmd file that do not include any testing R code chunk.
  - Make sure to test the **reproducibility** of your Rmd file before submission, which can be done (1) restart RStudio, (2) load your Rmd file into RStudio, and (3) execute each R code chunk one by one. 

```{r}
library(tidyverse)
```

### 1. Create a tibble from babyNames.csv (1 point)

```{r}
baby_names <- read_csv("babyNames.csv")
```

Examine`baby_names` to find out column names, column types and first several values in the column. 

```{r}
glimpse(baby_names)

```

### 2. Examine popularity of your name (1 point)

- If you don't have an English name, choose an English name you like.
- Arrange baby names in the descending order of the popularity (`Count`).

```{r}
baby_names %>% 
  filter(Name == "Jenny")%>%
  arrange(desc(Count))
```

### 3. Find the most popular name when you were born (1 point)

- If you are male (female), only examine boy's (girl's) names.

```{r}
baby_names %>%
  filter(Sex == "Girls" & Year == "1990") %>%
  top_n(1,Count)
```

### 4. Use ggplot2 to find peak popularity of your name (1 point)

- A line plot showing popularity of Michael (Boy) vs. year

```{r}
baby_names %>%
  group_by(Name) %>%
  filter(Name == "Jenny" & Sex == "Girls") %>%
  ggplot(aes(Year, Count))+
  geom_point() + geom_line() +
  xlab("Year") + 
  ylab("Count")
```

### 5. Find the year in which your name was most popular (2 point)

```{r}
baby_names %>% 
  filter(Name == "Jenny" & Sex =="Girls") %>%
  arrange(desc(Count))%>%
  top_n(1,Count)
```

### 6. Create a plot showing the most popular baby name (boys and girls) by proportion over the years (3 points)

Instead of using `Count`, use **proportion** as a measure of popularity. 

- Each year, find the most popular baby names for boys and girls; and compute the proportion of those names (relative to all baby names in that particular year); and repeat this process for all years in the data set.
  - Most popular name can change year by year. 


```{r}
# find the most popular baby names for boys and girls and compute the proportion of those names for all years in the data set. 
# In this code, I do it separately for boys and girls.
boy_stat<-
baby_names %>% 
  filter(Sex=="Boys")%>%
  group_by(Year, Sex)%>%
  summarize(Name, Sex, Count, Year, Prop=Count/sum(Count))%>%
  arrange(desc(Prop))%>%
  top_n(1,Prop)%>%
  arrange(desc(Year))

girl_stat<-
baby_names %>% 
  filter(Sex=="Girls")%>%
  group_by(Year, Sex)%>%
  summarize(Name, Sex, Count, Year, Prop=Count/sum(Count))%>%
  arrange(desc(Prop))%>%
  top_n(1,Prop)%>%
  arrange(desc(Year))

# Then, I merge boys and girls into one data frame.
baby_stat <- merge(boy_stat, girl_stat, by='Year')

# Create a plot showing the most popular baby name (boys and girls) by proportion over the years
ggplot(baby_stat, aes(x=Year))+
  geom_line(aes(y=Prop.x, color='Boys')) + geom_point(aes(y=Prop.x, color='Boys')) +
  geom_line(aes(y=Prop.y, color='Girls')) + geom_point(aes(y=Prop.y, color='Girls')) +
  scale_color_manual(name = "Sex", values = c("Boys" = "tomato", "Girls" = "skyblue")) +
  xlab("Year") + 
  ylab("Propotion")
```

