---
title: 'Assignment 3: Exloratory Data Analysis & Data Visualization'
output:
  html_document:
    df_print: paged
  pdf_document: default
---

1. Save this Rmd file as 'assignment3_yourfirstname_yourlastname.Rmd` (e.g., assignment3_youngjin_lee.Rmd).
2. Provide R codes that will create a data frame or generate each ggplot outcomes shown in the `assignment3_expected_results.html` file.
3. Submit your Rmd file and rendered HTML report file to Canvas. 
  - Make sure to submit a **clean** Rmd file that do not include any testing R code chunk.
  - Make sure to test the **reproducibility** of your Rmd file before submission, which can be done (1) restart RStudio, (2) load your Rmd file into RStudio, and (3) execute each R code chunk one by one. 

```{r message=FALSE}
library(tidyverse)
```

### 1. Create a data frame from a CSV file (1 point)

- Use the `mpg.csv` file to create a data frame that will be used in the subsequent tasks.
- Create a data frame (or tibble) named `df` from the `mpg.csv` file.

```{r}
  mympg <- read.csv("C:\\Users\\junhe\\Desktop\\Documents\\2021Fall semester\\LTEC6514_2021Fall\\LTEC6514_2021Fall\\mpg.csv")
  df <- data.frame(mympg)
```

```{r}
head(df)
```

- `manufacturer`: Car manufacturer
- `model`: Model name
- `displ`: Engine displacement in liters
- `year`: Year of manufacturing
- `cyl`: Number of cylinders
- `trans`: Type of transmission
- `drv`: Drive type
- `cty`: City mileage
- `hwy`: Highway mileage
- `fl`: Fuel type
- `class`: Vehicle class

### 2. Create a histogram of your data set (2 points)

- You need to find an appropriate ggplot2 function that will create a histogram of highway mileage.
  - Use the data frame (or tibble) you created in the previous step, 
  - You can use R help on ggplot2 or [ggplot2 cheatsheet](https://www.rstudio.com/wp-content/uploads/2015/03/ggplot2-cheatsheet.pdf) to find an appropriate ggplot2 function for this task
- Use `gray60` for `color` and `cornsilk` for `fill` aesthetics of the histogram.
- Use `Highway Mileage` for X axis label, and `Count`for Y axis label.

```{r}
ggplot(data=df, mapping = aes(hwy))+
  geom_histogram (color= "gray60", fill="cornsilk")
  
```

### 3. Create separate histograms of vehicle's city mileage for each vehicle class (2 points)

- You need to find an appropriate ggplot2 function that will create a histogram.
- Use `City Mileage` and `Count` for X and Y axis label
- Use `gray60` for `color` and `cornsilk` for `fill` aesthetics of the histogram.

```{r}
ggplot(df, aes(cty))+
  geom_histogram (color= "gray60", fill="cornsilk")+
  facet_wrap(~ class, nrow = 3)
```

### 4. Compare distributions of city mileage of vehivles by vehicle class (2 points)

- Use box plots to compare distributions 
- Use `City Mileage` for X axis label and `Vehicle Class` for Y label

```{r}
ggplot(data = df, 
       mapping = aes(x = cty, y = class)) + 
  geom_boxplot()+
  xlab("City Mileage")+
  ylab("Vehicle Class")
```

### 5. Create a scatter plot showing the relationship between city mileage and highway mileage (3 points)

- Use `City Mileage` and `Highway Mileage` for X and Y axis labels
- Show a straight (regression) line between city mileage and highway mileage
- Avoid overplotting

```{r}
ggplot(df, aes(cty, hwy)) + 
  geom_point(mapping = aes(cty, hwy),position = "jitter")+
  geom_smooth(method = "lm")+
  xlab("City Mileage")+
  ylab("Highway Mileage")
```

### 6. Examine whether this relationship (city mileage vs. highway mileage) is different by vehicle class (3 points)

- Use `City Mileage` and `Highway Mileage` for X and Y axis labels
- Use `color` aesthetics to reveal the difference
- Show one regression line between city mileage and highway mileage
- Avoid overplotting

```{r}
ggplot(df, aes(cty, hwy)) + 
  geom_point(mapping = aes(cty, hwy, color=class),position = "jitter")+
  geom_smooth( method = "lm")+
  xlab("City Mileage")+
  ylab("Highway Mileage")
```

### 7. Create separate regerssion plots (city mileage vs. highway mileage) for each vehicle class (3 points)

- Use `City Mileage` and `Highway Mileage` for X and Y axis labels
- Show a straight (regression) line for each vehicle class
- Use `size = 1` and `alpha = 0.5` when plotting points
  - Read R documentations to find out what `size = 1` and `alpha = 0.5` mean

```{r}
ggplot(df, aes(cty, hwy, color = "class")) +
  geom_point(mapping = aes(cty, hwy, color=class),size =1, alpha = 0.5, position = "jitter") +
  facet_wrap(~ class, nrow = 3)+
  geom_smooth( method = "lm") +
  xlab("City Mileage")+
  ylab("Highway Mileage")
  
```

