---
title: 'Assignment 1: Reproducible Research'
output:
  html_document:
    df_print: paged
---

## Objective

To practice how to conduct reproducible research using R Markdown

## What to do

1. Rename this Rmd file as `assignment1_yourfirstname_lastname.Rmd` (e.g., `assignment1_youngjin_lee.Rmd`).
2. Read the provided explanations and fill up the blank code chunks.
3. After completing the task, (1) make sure to remove **all intermediate** code chunks you used during the problem solving processes; and (2) create an HTML report.
  - If you don't remove intermediate code chunks, you will lose some points.
  - If your Rmd file fail to produce an HTML report, you will get **zero** point. 
4. Submit your Rmd file (\*.Rmd) and HTML report file (\*.html) to Canvas.

## Load ggplot2 package

```{r}
library(ggplot2)
```

## Create two numeric vectors (1 point)

- `x`: Hold integer values from -30 to 30 (i.e., -30, -29, -28, ..., 0, 1, ..., 29, 30)
- `y`: Hold $x^4$ values 

```{r}
  x <- -30:30
  y <- x^4
```


```{r}
x
```

```{r}
y
```

## Create a scatter plot showing (x, y) values (1 point)

- Use a `ggplot2` function explained in the book to create a scatter plot

```{r}
qplot(x,y)
```

## Create a function that creates a scatter plot, given a vector of numbers and the power value (2 point)

- Function name: `create_plot`
- Function argument 1: `x`, a numeric vector of any length
- Function argument 2: `n`, an exponent (or power) that will be used to create another vector by raising `x` to the power of `n`

```{r}
create_plot <- function (x, n) {
  y <- x^n
  qplot(x, y)
}
```

## Test `create_plot` function (1 point)

```{r}
create_plot(x, 2)
```

```{r}
create_plot(x, 3)
```

```{r}
create_plot(-40:30, 5)
```
